(TEMP) Online Video Game Monetization Schemes and Its Relationship to the Consumers

### 2022-04-26 outputs/paper/paper.Rmd
Completed Model and Results section of paper.Rmd.

library(tidyverse)
library(knitr) # for kable()
library(ggplot2) # for graphs

@@

@@

Table \@ref(tab:table1) showcases a summary of the average spending of the
respondents, categorized into age groups and gender, in USD. Already, we observe
that there is a noticeably higher average for spending in the pearl shop 
compared to upfront package purchases.
Note that this difference could be potentially misleading; The large majority
of players do not spend much money in the pearl shop, and the exceedingly high
average pearl shop spending is inflated by a select few players who have
invested massive amounts of real world currency into the game. This issue is
further elaborated upon in Section \@ref(discussion).

```{r table1, echo=FALSE, warning=FALSE, message=FALSE}
# Create summary dataset
# Due to insufficient response counts,
#   remove the "other" gender group for this summary table
summary_tbl <- cleaned_data[-c(47,70,85,103,135),] |>
  group_by(age_group, gender) |>
  summarise(ps_mean = mean(ps_total),
            packages_mean = mean(packages_usd),
            playtime_mean = mean(playtime_total))

# Use kable to create the table
summary_tbl |>
  kable(
    caption = "Summary of Average Playtime and Spending in Upfront and Cash Shop
      Categories in Black Desert Online",
    col.names = c("Age Group",
                  "Gender",
                  "Avg PS Spending (USD)",
                  "Avg Package Spending (USD)",
                  "Avg Playtime (hrs)"),
    digits = 1,
    booktabs = TRUE,
    linesep = ""
  )

```
```{r}

@@

@@

### Gender of Characters

Gender-based appeal is a deep-rooted design pattern in most Korean MMOs.
(`FIND SOME SOURCE FOR THIS SHIT`)
Most cosmetic options are designed to appeal to the general playerbase and often
forfeits any semblance of practicality. This issue is very apparent in female
armor designs in Korean MMOs, and Black Desert Online is generally not an
exception to this. To see if these appeal-based design decisions truly have
any merit behind them, data was collected on the number of adult
female characters that each respondent has. The intent is to compare it with
their spending in cosmetic items, as briefly demonstrated in
Figure \@ref(fig:graph4).

```{r graph4, fig.cap="Number of female characters Versus Total Spending", echo=FALSE, warning=FALSE, message=FALSE, fig.width=8, fig.height=4}
# Create a scatterplot on number of female characters versus total spending
cleaned_data |>
  ggplot(aes(x = character_female, y = ps_cosmetic_usd)) +
  geom_point(size = 1.75, alpha = 0.1, color="red") +
  theme_minimal() +
  labs(x = "Spending on Value Pack in Pearl Shop (USD)",
       y = "Number of VPs Purchased on Central Market")
```

@@

\begin{equation}
Y_i = \beta_0 + \beta_1 X_i + \beta_2 X_i (\#eq:linm)
\end{equation}

The general assumption behind the consideration of this model is that
as a player spends more time in BDO, the more likely they are to spend more
real world currencies in exchange for in-game items. This could be due to their
need to continue using subscription-esque items that grant them boosts, or
due to the creation of more content in the game that requires real world
currencies to purchase (such as cosmetic items). Given the context of 
gender-based appeal in Korean MMOs such as BDO, there could also be a connection
between number of female characters and a player's spending in the pearl shop.
The null hypothesis of this model therefore seeks to explore whether there 
really is a statistically significant connection between the total amount
of money spent in-game and the factors mentioned above. 
Equivalently,

\begin{equation}
H_0: \beta_1, \beta_2 \neq 0
\end{equation}

Equation \@ref(eq:linm) represents the model used in this paper, where
$Y_i$, the dependent variable, is a player's total spending in pearl shop,
$\beta_0$ is the intercept, $\beta_1$ is the covariate of total playtime,
$\beta_2$ is the covariate of number of female characters the player has.

Since the dependent variable is continuous, a linear model is considered instead
of a logistic model. For the analysis in the rest of this section, the dataset
is split 80%/20% for training/testing purposes. The statistical programming 
language `R` [@citeR] is used to run this model and present the findings from
it.

@@

TODO; Concrete findings accompanied by graphs

@@

>>>>

library(tidyverse)
library(knitr) # for kable()
library(kableExtra)
library(ggplot2) # for graphs
library(modelsummary)
library(cowplot) # for side by side plots

@@

All tables and graphs presented in this paper are produced using the 
statistical programming language `R` [@citeR]. The `knitr` [@citeknitr] and
`kableExtra` [@citeKableE] packages are used for tables, and the `ggplot`
[@citeggplot2] package is used for graphs.

@@

Table \@ref(tab:table1) showcases a summary of the average spending of the
respondents, categorized into age groups, gender, and whether the respondent
obtained the free package for the game, in USD. Pearl Abyss, the developer and
publisher of BDO, frequently employs events and/or utilize collaborations
with other companies (e.g., twitch prime, anniversary event, etc)
to hand out free packages for the game, which simply
allows a player access to the game but grants no other benefits or items
(Other package tiers grant players various items and benefits).

Already, we observe
that there is a noticeably higher average for spending in the pearl shop 
compared to upfront package purchases.
Note that this difference could be potentially misleading; The large majority
of players do not spend much money in the pearl shop, and the exceedingly high
average pearl shop spending is inflated by a select few players who have
invested massive amounts of real world currency into the game. This issue is
further elaborated upon in Section \@ref(discussion).

```{r table1, echo=FALSE, warning=FALSE, message=FALSE}
# Create summary dataset
# Due to insufficient response counts,
#   remove the "other" gender group for this summary table
summary_tbl <- cleaned_data[-c(47,70,85,103,135),] |>
  group_by(age_group, gender, package_free) |>
  summarise(ps_mean = mean(ps_total),
            packages_mean = mean(packages_usd),
            playtime_mean = mean(playtime_total))

# Use kable to create the table
summary_tbl |>
  kable(
    caption = "Summary of Average Playtime and Spending in Upfront and Cash Shop
      Categories in Black Desert Online",
    col.names = c("Age Group",
                  "Gender",
                  "Has Free Package",
                  "Pearl Shop",
                  "Game Packages",
                  "Avg Playtime (hrs)"),
    digits = 1,
    booktabs = TRUE,
    linesep = ""
  ) |>
  add_header_above(c(" " = 3, "Average Spending (USD)" = 2, " " = 1))

@@

Figure \@ref(fig:graph9) plots the rated importance of VP, and BK and OM.
We can observe that there is a considerable number of respondents who consider
VP as extremely critical to their enjoyment of the game. At the same time,
we can see a large number of
respondents consider BK and OM largely unimportant to their enjoyment of the
game. This shows that subscription-esque items are not universally regarded
as equally valuable by the respondents.

```{r graph9, fig.cap="Rated Importance of Value Pack, and Blessing of Kamasylve and Secret Book of Old Moon",  echo=FALSE, warning=FALSE, message=FALSE, fig.width=8, fig.height=4}

cleaned_data |>
  ggplot() +
  geom_histogram(aes(x = importance_vp, fill = "VP"), bins = 10, alpha = 0.4) +
  geom_histogram(aes(x = importance_bkom, fill = "BK and OM"), bins = 10, alpha = 0.4) +
  guides(fill=guide_legend(title="Subscription Type", )) +
  labs(x = "Rated Importance of Subscription Items")
```

@@

### Gender of players and Characters

Gender-based appeal is a deep-rooted design pattern in most Korean MMOs.
(`FIND SOME SOURCE FOR THIS SHIT`)
Most cosmetic options are designed to appeal to the general playerbase and often
forfeits any semblance of practicality. This issue is very apparent in female
armor designs in Korean MMOs, and Black Desert Online is generally not an
exception to this. 
There are 13 adult female characters in BDO and 9 adult male characters.
To see if these appeal-based design decisions truly have
any merit behind them, data was collected on the number of adult
female characters that each respondent has. The intent is to compare it with
their spending in cosmetic items, as briefly demonstrated in
Figure \@ref(fig:graph4).

```{r graph4, fig.cap="Number of Female Characters Versus Total Spending", echo=FALSE, warning=FALSE, message=FALSE, fig.width=8, fig.height=4}
# Create a scatterplot on number of female characters versus total spending
cleaned_data |>
  ggplot(aes(x = character_female, y = ps_cosmetic_usd)) +
  geom_point(size = 1.75, alpha = 0.1, color="red") +
  theme_minimal() +
  labs(x = "Number of Adult Female Characters the Respondent has",
       y = "Spending on Cosmetic Items in Pearl Shop (USD)")
```

It can be observed in Figure \@ref(fig:graph5) that there are more respondents
whose main character in BDO is female than male at all age groups. 
This statistic may not
be surprising, given that male respondents similarly dominate all age groups,
as shown in Figure \@ref(fig:graph6). Nevertheless, this may grant some insight
into the targeted audience of Black Desert Online.

```{r graph5, fig.cap="Gender of Main Character Across Age Groups", echo=FALSE, warning=FALSE, message=FALSE, fig.width=8, fig.height=4}

cleaned_data |>
  ggplot() +
  geom_bar(aes(x = age_group, fill = gender_main), position = 'dodge') +
  labs(x = "Age Group", y = "Count")
```

```{r graph6, fig.cap="Gender of Respondent Across Age Groups", echo=FALSE, warning=FALSE, message=FALSE, fig.width=8, fig.height=4}

cleaned_data |>
  ggplot() +
  geom_bar(aes(x = age_group, fill = gender), position = 'dodge') +
  labs(x = "Age Group", y = "Count")
```

@@

Since the dependent variable is continuous, a linear model is considered instead
of a logistic model.
We will be considering both the player's rated importance of VP and BKOM,
the number of female characters they have, and their
total playtime as explanatory variables as part of a multiple linear regression
model.
For the analysis in the rest of this section, the dataset
is split 80%/20% for training/testing purposes. The statistical programming 
language `R` [@citeR] is used to run this model and present the findings from
it.

\begin{equation}
Y = \beta_0 + \beta_1 X_1 + \beta_2 X_2 + \beta_3 X_3 + \beta_4 X_4 (\#eq:linm)
\end{equation}

The general assumption behind the consideration of this model is that
as a player spends more time in BDO, the more likely they are to spend more
real world currencies in exchange for in-game items. This could be due to their
need to continue using subscription-esque items that grant them boosts, or
due to the creation of more content in the game that requires real world
currencies to purchase (such as cosmetic items). Given the context of 
gender-based appeal in Korean MMOs such as BDO, there could also be a connection
between number of female characters and a player's spending in the pearl shop.
The model therefore seeks to explore whether there 
really is a statistically significant connection between the total amount
of money spent in-game and the factors mentioned above. 
Equivalently,

\begin{equation}
H_0: \beta_1 = \beta_2 = \beta_3 = \beta_4 = 0
\end{equation}

Equation \@ref(eq:linm) represents the model used in this paper, where
$Y$, the dependent variable, is a player's total spending in pearl shop,
$\beta_0$ is the intercept, $X_1$ is the covariate of total playtime,
$X_2$ is the covariate of number of female characters the player has.
$X_3$ is the covariate of the player's rated importance of VP.
$X_4$ is the covariate of the player's rated importance of BK and OM.
$\beta_1 \beta_2, \beta_3, \beta_4$ are the coefficients of the variables.

```{r model, fig.cap="Model Diagnostic Plots", echo=FALSE, warning=FALSE, message=FALSE, fig.width=9, fig.height=7}
# Split data into training and testing set
set.seed(6607)
train_samp <- sample(seq_len(nrow(cleaned_data)),
                     size = floor(0.8 * nrow(cleaned_data)))

train <- cleaned_data[train_samp,]
test <- cleaned_data[-train_samp,]

# Run linear model
# treat character_female as a numeric vector
train <- train |>
  mutate(character_female = (as.numeric(character_female)-1))
test <- test |>
  mutate(character_female = (as.numeric(character_female)-1))

lin_model <- lm(ps_total ~ importance_vp + importance_bkom
                + character_female + playtime_total,
                data = train)

# Run diagnostics
par(mfrow = c(2, 2))
plot(lin_model)

# Run another linear model
lin_model2 <- lm(ps_total ~ importance_vp + importance_bkom
                 + character_female + playtime_total,
                data = train[-c(91,62,19),])

lm_sum <- summary(lin_model2)

# Check predictions on testing dataset
linpred <- predict(lin_model2, test, type="response", se.fit = TRUE)
# Check mean squared error
mse <- mean((linpred$fit - test$ps_total)^2)
```

The diagnostic plots of the model are shown in Figure \@ref(fig:model).
The fitted values vs. residuals graph (top-left) shows a roughly horizontal line without
noticeable patterns, which indicated a linear relationship between the dependent
and independent variable.

The Normal Q-Q plot (top-right) shows most points falling on the dashed line,
though there are also a considerable number of points that fall off the dashed line
on the right tail end, suggesting that the residuals may not be entirely normally
distributed.

The Scale-Location plot (bottom-left) shows a red line that is not
horizontal, meaning that the variance of the residual
varies as the fitted value changes
This suggests that there may be a violation of
the homoscedasticity assumption which assumes that variance of
residuals is the same for all X values.
An alternative model with square-root transformation
of the dependent variable was attempted, but heteroscedasticity remained.

Note that points 91, 62 and 19 are all marked as possible outliers in the
three plots mentioned above, suggesting that their inclusion impacts the
linear model greatly. As such, they were removed in the final model.
The diagnostic conclusions remained similar to the ones above after the removal
of the said points.

The residuals vs. leverage plot (bottom-right) identifies two outliers that
greatly exceed the Cook's distance--points 91 and 62--and
one influence point at point 113 The removal of point 66 did not greatly affect
the overall trend shown by the red line in the same plot, thus it was kept in
the final model.

The model is used to predict pearl shop spending using the test dataset and
arrives at a mean squared error value of `967085.46`. This large MSE may be
due to outliers similar to the ones removed during the model diagnostics
section.

@@

## Model Summary

A summary plot shown in Table \@ref(tab:table2) is generated using the
`modelsummary` package [@citeModelSum] in `R` [@citeR].
Model 1 is the model including the outliers and Model 2 is the final model.

```{r table2, echo=FALSE, warning=FALSE, message=FALSE}
# Create model summary table
modelsummary(list(lin_model, 
                  lin_model2),
             fmt = 2,
             title = "Model Summary of Pearl Shop Spending Based on Rated
             Importance of VP, BK and OM, Number of Female Characters, and
             Total Playtime",
             output = 'markdown')
```

The coefficient estimates shown in Table \@ref(tab:table2) for the final model
is equivalent to the following, shown in Equation \@ref(eq:fitted):

\begin{equation}
\hat{Y_i} = -785.22 + 0.06 X_{1i} + 58.62 X_{2i} + 91.71 X_{3i}
  + 69.28 X_{4i}  (\#eq:fitted)
\end{equation}

Summary of the model shows that only the rated importance of Value Pack and 
the total playtime were statistically significant predictors
at $\alpha=0.01$ significance level. The rated importance of Blessing of
Kamasylve and Secret Book of Old Moon, and the number of female characters were
not statistically significant predictors.

## Character Gender Inequality

As alluded to in Section \@ref(gender-of-players-and-characters), gender-based
aesthetics are a major selling point of Korean MMOs such as BDO.
Figure \@ref(fig:graph7) plots the respondents' total spending in the pearl shop
against the proportion of the said spending contributed to cosmetic items.
The graph shows that on average, a player with a female main
character spends a higher proportion of their pearls on cosmetic items.
Specifically, on average, players with a female main character spends roughly an
additional 9.23% percent of their total pearl shop spending when compared to
players with a male main character.
This implies that for games focused on adding more cosmetic content to their
in-game cash shop, these cosmetics attract more customers if they were created
for female playable characters.

```{r graph7, fig.cap="Cosmetic Spending Versus Functional Spending in Pearl Shop", echo=FALSE, warning=FALSE, message=FALSE, fig.width=8, fig.height=4}

# Create new column that shows proportion of total pearl shop spending on
#   cosmetic items
# Exlucde point 193 as outlier for visually clearer graph
cleaned_data <- cleaned_data |>
  mutate(cos_prop = ps_cosmetic_usd / ps_total)

cleaned_data |>
  ggplot(aes(x=ps_total, y=cos_prop, color=gender_main)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(x = "Total Spending in Pearl Shop (USD)", y = "Proportion of Total
       Spending on Cosmetics")

# Check difference in average cosmetic item proportion
diff.avg.cos.prop <- 
  mean(cleaned_data[cleaned_data$gender_main=="Female"&cleaned_data$ps_total!=0,]$cos_prop) -
  mean(cleaned_data[cleaned_data$gender_main=="Male"&cleaned_data$ps_total!=0,]$cos_prop)
```

## Free Game Package

As shown in Table \@ref(tab:table1), some of the respondents had obtained the
free package for the game, which were frequently given out through various
methods by the developer and publisher of BDO, as described in Section
\@ref(preliminary-analysis). Out of the 67 respondents
who obtained the free package of the game, 23 of them remained completely
free-to-play and did not spend any real world currency to purchase in-game
items nor other game packages.
The other 44 respondents--almost double those who remained completely
free-to-play--either purchased in-game items on the pearl shop or other game
packages.

This is further elaborated upon in Table \@ref(tab:table3), which summarises
the dataset based on whether the respondent's spending status is considered
`completely free` if they obtained the free package for the game and did not
spent money on other game packages nor in the pearl shop, and `partially free`
if they obtained the free package for the game but spent money on other
game packges and/or in the pearl shop.
We can see from Table \@ref(tab:table3) that despite having a lower average
spending in both the pearl shop and game packages, the "partially free" players
still spent a substantial amount of money on further purchases for the game:
On average, for "partially free" respondents,
the amount of money spent on game package purchases accounts for only 6% of
their total spending on BDO. We observe a similar statistic for players who
did not obtain a free package for the game, whose spending on game packages
accounts for only 5% of their total spending on BDO.

```{r table3, echo=FALSE, warning=FALSE, message=FALSE, fig.width=8, fig.height=4}
# create column to mark completely free-to-play respondents
cleaned_data <- cleaned_data |>
  mutate(comp_free = 
           ifelse((package_free==1 & ps_total==0 & packages_usd==0),"yes","no"))

# create column to mark respondents who got the game for free but still 
#   paid for in-game items
cleaned_data <- cleaned_data |>
  mutate(part_free = 
           ifelse((package_free==1 & (ps_total!=0 | packages_usd!=0)),"yes","no"))

summary_tbl2 <- cleaned_data |>
  group_by(comp_free, part_free) |>
  summarise(ps_mean = mean(ps_total),
            packages_mean = mean(packages_usd),
            pack_ps_percent = mean(packages_usd)/(mean(ps_total)+mean(packages_usd)),
            vp_ps_percent = mean(ps_vp_usd)/(mean(ps_total)+mean(packages_usd)),
            bkom_ps_percent = mean(ps_bkom_usd)/(mean(ps_total)+mean(packages_usd)))

# Use kable to create the table
summary_tbl2 |>
  kable(
    caption = "Summary of Average Playtime and Spending in Upfront and Cash Shop
      Categories in Black Desert Online Based On Free Package Acquisition",
    col.names = c("Completely Free",
                  "Partially Free",
                  "Pearl Shop",
                  "Packages",
                  "Packages",
                  "VP",
                  "BKOM"),
    digits = 2,
    booktabs = TRUE,
    linesep = ""
  ) |>
  add_header_above(c("Spending Status" = 2,
                     "Average Spending (USD)" = 2,
                     "Average Proportion of Total Spending" = 3))
```

## Subscription Items

As discussed in \@ref(preliminary-analysis), Figure \@ref(fig:graph9) suggests
a difference in importance as regarded by the respondents. This is supported
by the statistics shown in Figure \@ref(fig:graph8), which show a stronger
positive linear correlation between rated importance of VP and spending on
VP when compared to the correlation between rated importance of BK and OM and
spending on BK and OM. On average, respondents spend $148.0288 USD on
purchasing VP from the pearl shop, and spend $49.1202 USD on purchasing
BK and OM from the pearl shop.

Table \@ref(tab:table3) shows that on average, VP accounts for 11% of
a respondent's total spending on BDO (15% for partially free respondents).
BK and OM accounts for 4% of a respondent's total spending on BDO (5% for
partially free respondents).

```{r graph8, fig.cap="Rated Importance of Subscription Items Versus Spending on the Said Items",  echo=FALSE, warning=FALSE, message=FALSE, fig.width=8, fig.height=4}
# Create scatterplot for rated importance of VP vs. USD spent on VP
# Remove row 60 for a visually clearer graph
plot1 <- cleaned_data[-60,] |>
  ggplot(aes(x = importance_vp, y = ps_vp_usd)) +
  geom_point(size = 1.75, alpha = 0.1, color="red") +
  geom_smooth(method = "lm", se = FALSE) +
  theme_minimal() +
  labs(x = "Importance of VP",
       y = "Spending on VP in Pearl Shop (USD)")

# Create scatterplot for rated importance of VP vs. USD spent on VP
plot2 <- cleaned_data |>
  ggplot(aes(x = importance_vp, y = ps_vp_usd)) +
  geom_point(size = 1.75, alpha = 0.1, color="red") +
  geom_smooth(method = "lm", se = FALSE) +
  theme_minimal() +
  labs(x = "Importance of BK and OM",
       y = "Spending on BK and OM in Pearl Shop (USD)")

plot_grid(plot1, plot2)

mean_vp <- mean(cleaned_data$ps_vp_usd)
mean_bkom <- mean(cleaned_data$ps_bkom_usd)
```

@@

## Free Game Versus Upfront Cost

The statistics presented in Table \@ref(tab:table3) suggests that
the amount of revenue obtained from game package purchases is relatively
minuscule compared to other sources of income. Therefore, publishers of
MMORPGs should forgo charging an upfront fee for their games in order to draw
in more players so that they can browse the much more profitable in-game cash
shop instead.
